---
title: "Hidden vs Visible Resources in the Survival Game (Experiment 2)"
author: Scott Claessens
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```

# 0. Setup

Load the data from Study 2. 

```{r echo=F}
readd(d2.00)
```

Each row is a different participant in Study 2 (there were 80). Columns 1-68 are variables that summarise the whole session. Columns 69-493 refer to events in each round of the Visible condition. Columns 494-918 refer to the Hidden condition. This experiment followed a within-subjects design (i.e. participants completed both the Hidden and Visible conditions). In the counterbalancing column, 0 means that the participant played the Visible game before the Hidden game, and 1 means that the participant played the Hidden game before the Visible game.

# 1. Binomial - Number of shocks

Trim the dataset and get it in long-format.

```{r echo=F}
readd(d2.01)
```

As in Study 1, we first test whether the probability of a shock occurring differs between the two conditions. Although this experiment followed a within-subjects design, random effects are not necessary here because the occurrence of shocks are independent between the two conditions.

All analyses in this document will use the `brm()` function. Learn more about the **brms** package [here](https://github.com/paul-buerkner/brms).

```{r echo=F}
fitModel2.01
```

We set the `seed` to a random number, to make the results reproducible. Here are the priors that were set for this model.

```{r echo=F}
readd(priors2.01)
```

Let's look at the results.

```{r echo=F}
print(readd(m2.01))
```

Plotting the parameters.

```{r echo=F, fig.height = 2, fig.width = 7}
readd(pars2.01)
```

The Condition parameter is -0.04, and its 95% credible intervals cross 0, implying that the probability of a shock is no different across the two conditions. On the probability scale:

```{r}
post <- readd(post2.01)

visible_prob <- inv_logit_scaled(post$b_Intercept)
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)
difference   <- hidden_prob - visible_prob

quantile(difference,c(0.025,0.5,0.975)) %>% round(2)
```

# 2. Gaussian - Total amount of cattle lost due to shocks

Trim the dataset again.

```{r echo=F}
readd(d2.02)
```

We now fit a model to determine if the total amount of cattle lost due to shocks varies between conditions. Again, no random effects are needed because the outcome is independent across conditions (generated stochastically by the game), despite the within-subject design.

```{r echo=F}
fitModel2.02
```

The priors we used.

```{r echo=F}
readd(priors2.02)
```

The results.

```{r echo=F}
print(readd(m2.02))
```

Plot the parameters.

```{r echo=F, fig.height=2, fig.width=7}
readd(pars2.02)
```

On average, 7 more cattle were lost in the Hidden condition than the Visible condition.

# 3. Binomial - Probability of requesting

Get a long-format data frame with binary request decisions over all rounds, for both conditions. If request == NA, player has died and been removed from the game, so we drop those rows.

```{r echo=F}
readd(d2.03)
```

This leaves us with 2834 request decisions.

We now fit a varying intercept and slope model, with participants nested within groups. We allow the slopes for both round number *and* condition to vary, to fit with the experiment's within-subjects design (participants completed multiple rounds, in both conditions).

```{r echo=F}
fitModel2.03
```

Here are the priors for the model we just fitted.

```{r echo=F}
readd(priors2.03)
```

Now let's see the results.

```{r echo=F}
print(readd(m2.03))
```

Plotting the parameters.

```{r echo=F}
readd(pars2.03)
```

Finally, let's see the trace plots.

```{r echo=F}
plot(readd(m2.03), ask = F)
```

Looks like Stan sampled efficiently.

In this model, the fixed effect of condition is 0.63, with 95% credible intervals above 0. This implies that the participants are more likely to request from their partner in the Hidden condition. Converting to the probability scale:

```{r}
post <- readd(post2.03)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob

quantile(difference,c(0.025,0.5,0.975)) %>% round(2)
```

The absolute probability difference between the conditions is +0.14 (median), with 95% CIs above 0. Participants were more likely to request from their partner in the Hidden condition.

We compute a Bayes factor for this difference between probabilities. This is the inverse of the alternative hypothesis that the two conditions are equal.

```{r echo=F}
readd(bf2.03)
```

This Bayes factor implies weak support for the hypothesis that the probabilities differ across conditions.

# 4a. Binomial - Probability of requesting when above the minimum threshold

Get a long-format data frame with binary request decisions over all rounds, for both conditions. If request == NA, player has died and been removed from the game, so we drop those rows. However, we also filter out rows in which the player was below the minimum survival threshold (64 cattle).

```{r echo=F}
readd(d2.04)
```

This leaves us with 2368 request decisions.

We now fit a varying intercept and slope model, with participants nested within groups. Again, we allow the slopes for both round number *and* condition to vary.

```{r echo=F}
fitModel2.04a
```

The priors.

```{r echo=F}
readd(priors2.04a)
```

The results.

```{r echo=F}
print(readd(m2.04a))
```

Creating a forest plot of parameters.

```{r echo=F}
readd(pars2.04a)
```

Trace plots.

```{r echo=F}
plot(readd(m2.04a), ask = F)
```

Looks like Stan sampled efficiently.

In this model, the fixed effect of condition is 0.19, with 95% credible intervals crossing 0. This implies that, at least when above the minimum survival threshold, the average probability of requesting did not differ between conditions.

Converting the fixed effects to the probability scale:

```{r}
post <- readd(post2.04a)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob

quantile(difference,c(0.025,0.5,0.975)) %>% round(2)
```

The absolute probability difference between the conditions is +0.02 (median), with 95% CIs above 0. Participants were no more likely to request from their partner in the Hidden condition.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.04a)
```

This Bayes factor implies moderate support for the hypothesis that the probabilities are _equal_ in each condition.

# 4b. Binomial - Probability of requesting when above the minimum threshold (interacting with counterbalancing)

We found no effect of condition in the previous model. Is this because of order effects?

```{r echo=F}
fitModel2.04b
```

The priors.

```{r echo=F}
readd(priors2.04b)
```

The results.

```{r echo=F}
print(readd(m2.04b))
```

Creating a forest plot of parameters.

```{r echo=F}
readd(pars2.04b)
```

Trace plots.

```{r echo=F}
plot(readd(m2.04b), ask = F)
```

Looks like Stan sampled efficiently.

In this model, the interaction parameter is 1.55, with 95% CIs above zero. This implies that there is an interaction effect. Condition only has an effect on cheating when participants played the Hidden game first.

Converting the fixed effects to the probability scale:

```{r}
post <- readd(post2.04b)

visible_VisibleFirst_prob <- inv_logit_scaled(post$b_Intercept)

visible_VisibleFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_VisibleFirst_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_VisibleFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
difference_VisibleFirst <- hidden_VisibleFirst_prob - visible_VisibleFirst_prob

quantile(difference_VisibleFirst,c(0.025,0.5,0.975)) %>% round(2)
```

When participants play the Visible game first, the absolute probability difference between the conditions is -0.03 (median), with 95% CIs crossing 0. Participants were no more likely to request from their partner in the Hidden condition.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.04b1)
```

This Bayes factor implies moderate support for the hypothesis that the probabilities are equal in each condition.

What about for when participants play the Hidden game first?

```{r}
visible_HiddenFirst_prob <- inv_logit_scaled(post$b_Intercept + post$b_Counterbalancing)

visible_HiddenFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_HiddenFirst_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Counterbalancing + 
                                          post$b_Condition + post$`b_Condition:Counterbalancing`)

hidden_HiddenFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
difference_HiddenFirst <- hidden_HiddenFirst_prob - visible_HiddenFirst_prob

quantile(difference_HiddenFirst,c(0.025,0.5,0.975)) %>% round(2)
```

When participants play the Hidden game first, the absolute probability difference between the conditions is +0.20 (median), with 95% CIs above 0. Participants are more likely to request from their partner when beneath the threshold in the Hidden condition.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.04b2)
```

This Bayes factor implies moderate support for the hypothesis that the probabilities differ across conditions.

# 5. Binomial - Probability of not responding to a request

Get long-format data frame with 'received' variable (i.e. how much a player received on any given round). We swap this around so it reflects how much the player *gave* to their partner (i.e. how much their partner received). We drop rows with NAs, since partners did not request help in that particular round. We then code whether the player gave nothing in response to the request (1) or gave at least one cattle (0).

```{r echo=F}
readd(d2.05)
```

This leaves us with 716 possible responses to requests.

We then fit the varying intercept and slope model, again with participants nested within groups.

```{r echo=F}
fitModel2.05
```

The priors we used.

```{r echo=F}
readd(priors2.05)
```

The results.

```{r echo=F}
print(readd(m2.05))
```

Plotting the parameters.

```{r echo=F}
readd(pars2.05)
```

Let's look at the trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m2.05), ask = F)
```

Rhat values, n_eff values, and trace plots look okay.

The fixed effect of condition is 0.49, with 95% credible intervals that cross 0. This implies that participants were no more likely to not respond to requests in the Hidden condition.

As before, we sample from the posterior and convert this difference to the absolute probability scale.

```{r}
post <- readd(post2.05)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob

quantile(difference,c(0.025,0.5,0.975)) %>% round(2)
```

The probability difference between the conditions is 0.07 (median), with 95% CIs crossing 0.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.05)
```

This Bayes factor implies anecdotal support for the hypothesis that the probabilities are equal across conditions.

# 6a. Binomial - Probability of fulfilling a request when able

Again, the data wrangling for this model is a little trickier.

1. First, we get a long-format data frame with (a) the player's herd size that round, (b) how much the player received that round, and (c) how much the player requested that round.
2. Next, we flip the latter two variables to get (b') how much the *player gave*, and (c') how much the *player's partner requested*. 'Flipping' is possible because partners sit next to the focal player in the data frame.
3. We drop rows with NAs, as no requesting happened this round.
4. We keep only rows in which the partner's request could be fulfilled without dropping the player below the minimum survival threshold (i.e. the player was *able* to give).
5. Finally, we code whether the player fulfilled the request by giving what was asked or more (0) or did not fulfill the request (1).

```{r echo=F}
readd(d2.06)
```

This leaves us with 473 possible response decisions in which the player was able to give their partner what they asked for. Our outcome variable is whether they fulfilled that request or not.

We now fit the varying intercept and slope model, again with participants nested within groups.

```{r echo=F}
fitModel2.06a
```

Here are the priors we used.

```{r echo=F}
readd(priors2.06a)
```

Let's see the results.

```{r echo=F}
print(readd(m2.06a))
```

Plotting the parameters.

```{r echo=F}
readd(pars2.06a)
```

Let's look at the trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m2.06a), ask = F)
```

Stan sampled efficiently.

The fixed effect of condition is 0.94, with 95% credible intervals above 0. This implies that participants were more likely to not fulfill requests (when able) in the Hidden condition. 

On the absolute probability scale.

```{r}
post <- readd(post2.06a)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob

quantile(difference,c(0.025,0.5,0.975)) %>% round(2)
```

The probability difference between the conditions is 0.23 (median), with 95% CIs above zero.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.06a)
```

This Bayes factor implies moderate support for the hypothesis that the probabilities differ across conditions.

# 6b. Binomial - Probability of fulfilling request when able (interacting with counterbalancing)

As before, we test for order effects by including an interaction.

```{r echo=F}
fitModel2.06b
```

Here are the priors we used.

```{r echo=F}
readd(priors2.06b)
```

Let's see the results.

```{r echo=F}
print(readd(m2.06b))
```

Plotting the parameters.

```{r echo=F}
readd(pars2.06b)
```

The interaction parameter has 95% CIs that cross zero, indicating no interaction effect.

Converting the fixed effects to the probability scale:

```{r}
post <- readd(post2.06b)

visible_VisibleFirst_prob <- inv_logit_scaled(post$b_Intercept)

visible_VisibleFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_VisibleFirst_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_VisibleFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
difference_VisibleFirst <- hidden_VisibleFirst_prob - visible_VisibleFirst_prob

quantile(difference_VisibleFirst,c(0.025,0.5,0.975)) %>% round(2)
```

When participants play the Visible game first, the absolute probability difference between the conditions is +0.15 (median), with 95% CIs crossing 0. Participants were no more likely to not fulfill their partner's request in the Hidden condition.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.06b1)
```

This Bayes factor implies anecdotal support for the hypothesis that the probabilities are different across conditions.

What about for when participants play the Hidden game first?

```{r}
visible_HiddenFirst_prob <- inv_logit_scaled(post$b_Intercept + post$b_Counterbalancing)

visible_HiddenFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_HiddenFirst_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Counterbalancing + 
                                          post$b_Condition + post$`b_Condition:Counterbalancing`)

hidden_HiddenFirst_prob %>%
  median() %>%
  round(2)
```

```{r}
difference_HiddenFirst <- hidden_HiddenFirst_prob - visible_HiddenFirst_prob

quantile(difference_HiddenFirst,c(0.025,0.5,0.975)) %>% round(2)
```

When participants play the Hidden game first, the absolute probability difference between the conditions is +0.26 (median), with 95% CIs above 0. Participants are more likely to not fulfill their partner's request in the Hidden condition.

We compute a Bayes factor for this difference between probabilities.

```{r echo=F}
readd(bf2.06b2)
```

This Bayes factor implies moderate support for the hypothesis that the probabilities differ across conditions.

# 7. Survival analysis - Condition

Get the data.

```{r echo=F}
readd(d2.07)
```

Fit the model.

```{r echo=F}
fitModel2.07
```

What priors did we use?

```{r echo=F}
readd(priors2.07)
```

Results.

```{r echo=F}
print(readd(m2.07))
```

Plot parameters.

```{r echo=F}
readd(pars2.07)
```

Trace plots.

```{r echo=F}
plot(readd(m2.07), ask = F)
```

For participants who play the Visible game first, estimate survival rate in Visible condition.

```{r}
post <- readd(post2.07)

set.seed(2113)
srateVisible <- rweibull(4000, post$shape, exp(post$b_Intercept))
median(srateVisible)
```

Estimate survival rate in Hidden condition.

```{r}
set.seed(2113)
srateHidden <- rweibull(4000, post$shape, exp(post$b_Intercept + post$b_Condition))
median(srateHidden)
```

```{r}
difference <- srateHidden - srateVisible
quantile(difference, c(0.025, 0.5, 0.975))
```

For participants who play the Hidden game first, estimate survival rate in Visible condition.

```{r}
set.seed(2113)
srateVisible <- rweibull(4000, post$shape, exp(post$b_Intercept + post$b_Counterbalancing))
median(srateVisible)
```

Estimate survival rate in Hidden condition.

```{r}
set.seed(2113)
srateHidden <- rweibull(4000, post$shape, exp(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`))
median(srateHidden)
```

```{r}
difference <- srateHidden - srateVisible
quantile(difference, c(0.025, 0.5, 0.975))
```

# 8. Survival analysis - Proportion of Rule 1 cheating

Load data.

```{r echo=F}
readd(d2.08)
```

Fit the model.

```{r echo=F}
fitModel2.08
```

What priors did we use?

```{r echo=F}
readd(priors2.08)
```

Results.

```{r echo=F}
print(readd(m2.08))
```

Plot parameters.

```{r echo=F}
readd(pars2.08)
```

Trace plots.

```{r echo=F}
plot(readd(m2.08), ask = F)
```

# 9. Survival analysis - Proportion of Rule 2 cheating

Load data.

```{r echo=F}
readd(d2.09)
```

Fit the model.

```{r echo=F}
fitModel2.09
```

What priors did we use?

```{r echo=F}
readd(priors2.09)
```

Results.

```{r echo=F}
print(readd(m2.09))
```

Plot parameters.

```{r echo=F}
readd(pars2.09)
```

Trace plots.

```{r echo=F}
plot(readd(m2.09), ask = F)
```

# 10. Herd size when requesting / not requesting

Get data.

```{r echo=F}
readd(d2.10)
```

Fit the model.

```{r echo=F}
fitModel2.10
```

What priors did we use?

```{r echo=F}
readd(priors2.10)
```

Results.

```{r echo=F}
print(readd(m2.10))
```

Trace plots.

```{r echo=F}
plot(readd(m2.10), ask = F)
```

We focus on participants who played the Hidden game first. 

For participants in the Visible condition, posterior herd size when not requesting:

```{r echo=F}
post <- readd(post2.10)

median(post$b_Intercept + post$b_Counterbalancing) %>% round(2)
```

And when requesting:

```{r echo=F}
median(post$b_Intercept + post$b_request + post$b_Counterbalancing + post$`b_Counterbalancing:request`) %>% round(2)
```

For participants in the Hidden condition, posterior herd size when not requesting:

```{r echo=F}
median(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`) %>% round(2)
```

And when requesting:

```{r echo=F}
median(post$b_Intercept + post$b_Condition + post$b_request + post$`b_Condition:request` + post$b_Counterbalancing + post$`b_Condition:Counterbalancing` + post$`b_Counterbalancing:request` + post$`b_Condition:Counterbalancing:request`) %>% round(2)
```

Does the herd size when requesting differ across conditions? Get the posterior difference.

```{r echo=F}
quantile(post$b_Condition + post$`b_Condition:request` + post$`b_Condition:Counterbalancing` + post$`b_Condition:Counterbalancing:request`, c(.025, .5, .975)) %>% round(2)
```

No.

# 11. Amount requested

Get data. We log the amount requested.

```{r echo=F}
readd(d2.11)
```

Fit the model.

```{r echo=F}
fitModel2.11
```

What priors did we use?

```{r echo=F}
readd(priors2.11)
```

Results.

```{r echo=F}
print(readd(m2.11))
```

Trace plots.

```{r echo=F}
plot(readd(m2.11), ask = F)
```

We focus on participants who played the Hidden game first.

How many cattle are requested on average by participants in the Visible condition?

```{r echo=F}
post <- readd(post2.11)
median(exp(post$b_Intercept + post$b_Counterbalancing)) %>% round(2)
```

And in the Hidden condition?

```{r echo=F}
median(exp(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`)) %>% round(2)
```

Do these amounts differ?

```{r}
quantile(exp(post$b_Intercept + post$b_Counterbalancing) - exp(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`), c(.025, .5, .975)) %>% round(2)
```

Not quite.

# 12. Difference between amount requested and amount needed

Get data. We calculate `diff` as the difference between the amount requested and the amount needed to reach the minimum survival threshold.

```{r echo=F}
readd(d2.12)
```

Fit the model.

```{r echo=F}
fitModel2.12
```

What priors did we use?

```{r echo=F}
readd(priors2.12)
```

Results.

```{r echo=F}
print(readd(m2.12))
```

Trace plots.

```{r echo=F}
plot(readd(m2.12), ask = F)
```

We focus on participants who played the Hidden game first.

What's the posterior `diff` score for participants in the Visible condition? A positive score indicates asking for "too many" resources, while a negative number indicates asking for "too few".

```{r echo=F}
post <- readd(post2.12)
quantile(post$b_Intercept + post$b_Counterbalancing, c(.025, .5, .975)) %>% round(2)
```

And for participants in the Hidden condition?

```{r echo=F}
quantile(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`, c(.025, .5, .975)) %>% round(2)
```

# 13. Difference between amount requested by partner and amount given

Get data. We calculate `diff` as the difference between the amount requested by one's partner and the amount given.

```{r echo=F}
readd(d2.13)
```

Fit the model.

```{r echo=F}
fitModel2.13
```

What priors did we use?

```{r echo=F}
readd(priors2.13)
```

Results.

```{r echo=F}
print(readd(m2.13))
```

Trace plots.

```{r echo=F}
plot(readd(m2.13), ask = F)
```

We focus on participants that played the Hidden game first.

What's the posterior `diff` score for participants in the Visible condition?

```{r echo=F}
post <- readd(post2.13)
quantile(post$b_Intercept + post$b_Counterbalancing, c(.025, .5, .975)) %>% round(2)
```

What about participants in the Hidden condition?

```{r echo=F}
quantile(post$b_Intercept + post$b_Condition + post$b_Counterbalancing + post$`b_Condition:Counterbalancing`, c(.025, .5, .975)) %>% round(2)
```

Difference between these.

```{r}
quantile(post$b_Condition + post$`b_Condition:Counterbalancing`, c(.025, .5, .975)) %>% round(2)
```

# Session Info

```{r}
sessionInfo()
```