---
title: "Hidden vs Visible Resources in the Survival Game (Experiment 3)"
author: Scott Claessens
date: "`r format(Sys.Date())`"
output:
  html_document:
    df_print: paged
    toc: true
    number_sections: false
    toc_float: true
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 120)
```

# 0. Setup

You'll need to download [Stan](http://mc-stan.org/) to your machine for these analyses.

Load in the data from Experiment 3.

```{r echo=F}
readd(d3.00)
```

Each row is a different participant in the study (there were 84). Columns 1-36 are variables that summarise the whole session, while the rest of the columns specify the events that occurred in each of the 25 rounds.

# 1. Binomial - Number of shocks

We'll trim the dataset, to make it more manageable.

```{r echo=F}
readd(d3.01)
```

In this dataset, Condition == 1 implies that the participant played the Survival Game in the 'Hidden' condition. Unlike in Study 1, 'Hidden' here means that Player 2's resources were hidden, while Player 1's resources were visible as normal. Condition == 0 refers to the standard 'Visible' control condition.

We first test whether the probability of a shock occurring differs between the two conditions. All analyses in this document will use the `brm()` function. Learn more about the **brms** package [here](https://github.com/paul-buerkner/brms).

```{r echo=F}
fitModel3.01
```

Priors.

```{r echo=F}
readd(priors3.01)
```

Let's look at the results.

```{r echo=F}
print(readd(m3.01))
```

The probability of a shock occuring does not differ across conditions.

# 2. Gaussian - Total amount of cattle lost due to shocks

Trim the dataset again.

```{r echo=F}
readd(d3.02)
```

We now fit a model to determine if the total amount of cattle lost due to shocks varies between conditions.

```{r echo=F}
fitModel3.02
```

The priors we used.

```{r echo=F}
readd(priors3.02)
```

The results.

```{r echo=F}
print(readd(m3.02))
```

The total amount of cattle lost does not vary between conditions.

# 3. Binomial - Probability of requesting

Get a long-format data frame with binary request decisions over all rounds. If request == NA, player has died and been removed from the game, so we drop those rows. We also retain only Player 2s.

```{r echo=F}
readd(d3.03)
```

This leaves us with 677 request decisions.

We now fit a varying intercept and slope model, grouped by participant. We only allow the slope for round number to vary, as participants completed multiple rounds (within-subjects) but only one condition, Hidden or Visible (between-subjects).

```{r echo=F}
fitModel3.03
```

Here are the priors for the model we just fitted.

```{r echo=F}
readd(priors3.03)
```

Now let's see the results.

```{r echo=F}
print(readd(m3.03))
```

Plotting the parameters.

```{r echo=F}
readd(pars3.03)
```

Trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m3.03), ask = F)
```

Looks like Stan sampled efficiently.

There seems to be no effect of condition on the probability of requesting for Player 2s. 

Let's sample from the posterior and convert to the probability scale.

```{r}
post <- readd(post3.03)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>% 
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob
quantile(difference, c(0.025, 0.5, 0.975)) %>% round(2)
```

Bayes factor for the difference between probabilities.

```{r echo=F}
readd(bf3.03)
```

This Bayes factor implies that we cannot be certain whether the difference between these probabilities is different or equal to zero, though it is verging on equal.

# 4. Binomial - Probability of requesting when above the minimum threshold

As before, get a long-format data frame with binary request decisions over all rounds. If request == NA, player has died and been removed from the game, so we drop those rows. However, we also filter out rows in which the player was below the minimum survival threshold (64 cattle). As before, we also retain only Player 2s.

```{r echo=F}
readd(d3.04)
```

This leaves us with 600 request decisions.

Fit the varying intercept and slope model, grouped by participant.

```{r echo=F}
fitModel3.04
```

Here are the priors for this model.

```{r echo=F}
readd(priors3.04)
```

Let's see the results.

```{r echo=F}
print(readd(m3.04))
```

Plotting the parameters.

```{r echo=F}
readd(pars3.04)
```

Trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m3.04), ask = F)
```

These HMC chains look healthy.

As with our previous model, it doesn't look like condition is having an effect. Get the probabilities of requesting while above the threshold (greediness) in both conditions.

```{r}
post <- readd(post3.04)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob
quantile(difference, c(0.025, 0.5, 0.975)) %>% round(2)
```

Greediness is comparable across conditions. Get a Bayes factor for this difference.

```{r echo=F}
readd(bf3.04)
```

This Bayes factor implies that we cannot be certain whether the probabilities are different or equal.

# 5. Binomial - Probability of not responding to a request

Get long-format data frame with 'received' variable (i.e. how much a player received on any given round). We swap this around so it reflects how much the player *gave* to their partner (i.e. how much their partner received). We drop rows with NAs, since partners did not request help in that particular round. We then code whether the player gave nothing in response to the request (1) or gave at least one cattle (0). Finally, we retain only Player 2s.

```{r echo=F}
readd(d3.05)
```

This leaves us with 194 possible responses to requests.

We then fit the varying intercept and slope model, again grouped by participant.

```{r echo=F}
fitModel3.05
```

Here are the priors for the model we just fitted.

```{r echo=F}
readd(priors3.05)
```

The results.

```{r echo=F}
print(readd(m3.05))
```

Plotting the parameters.

```{r echo=F}
readd(pars3.05)
```

Let's look at the trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m3.05), ask = F)
```

There's an effect of condition. Let's convert to probability scale.

```{r}
post <- readd(post3.05)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

What's the difference in probabilities between conditions?

```{r}
difference <- hidden_prob - visible_prob
quantile(difference, c(0.025, 0.5, 0.975)) %>% round(2)
```

Bayes Factor.

```{r echo=F}
readd(bf3.05)
```

This Bayes Factor provides weak support for the hypothesis that the probabilities differ.

# 6. Binomial - Probability of not fulfilling a request when able

The data wrangling for this model is a little trickier.

1. First, we get a long-format data frame with (a) the player's herd size that round, (b) how much the player received that round, and (c) how much the player requested that round.
2. Next, we flip the latter two variables to get (b') how much the *player gave*, and (c') how much the *player's partner requested*. 'Flipping' is possible because partners sit next to the focal player in the data frame.
3. We drop rows with NAs, as no requesting happened this round.
4. We keep only rows in which the partner's request could be fulfilled without dropping the player below the minimum survival threshold (i.e. the player was *able* to give).
5. We code whether the player fulfilled the request by giving what was asked or more (0) or did not fulfill the request (1).
6. We retain only Player 2s.

```{r echo=F}
readd(d3.06)
```

This leaves us with 138 possible response decisions in which the player was able to give their partner what they asked for. Our outcome variable is whether they fulfilled that request or not.

We now fit the varying intercept and slope model, grouped by participant ID.

```{r echo=F}
fitModel3.06
```

Here are the priors.

```{r echo=F}
readd(priors3.06)
```

Let's see the results.

```{r echo=F}
print(readd(m3.06))
```

Plotting the parameters.

```{r echo=F}
readd(pars3.06)
```

Let's look at the trace plots to make sure Stan sampled efficiently.

```{r echo=F}
plot(readd(m3.06), ask = F)
```

Again, the RHat values, n_eff values, and trace plots look okay.

Let's get estimates on the absolute probability scale.

```{r}
post <- readd(post3.06)

visible_prob <- inv_logit_scaled(post$b_Intercept)

visible_prob %>%
  median() %>%
  round(2)
```

```{r}
hidden_prob  <- inv_logit_scaled(post$b_Intercept + post$b_Condition)

hidden_prob %>%
  median() %>%
  round(2)
```

```{r}
difference <- hidden_prob - visible_prob
quantile(difference, c(0.025, 0.5, 0.975)) %>% round(2)
```

Bayes Factor.

```{r echo=F}
readd(bf3.06)
```

This Bayes Factor provides anecdotal support for the alternative (difference) over the null (no difference) hypothesis.

# Session Info

```{r}
sessionInfo()
```